% Identification of safety critical system components?
% Definition of simulation requirements & constraints
% Gamification strategy: what should the objective be, how should the user be engaged -> use the definition of Game to point this out
% Conceptual Design of Game Engine (Architecture & Features)
% Conceptual design of scenes / characters / challenges (goals, visual elements, structure)
% validation method used

\chapter{Conceptualization}\label{ch:design}
In this chapter, the game idea is presented.
All major elements of the game design process are defined and explained and requirements and constraints to the game are detailed, as well as
the structure of the framework of the game engine is described.

\section{Requirements}\label{sec:requirements}
As the major objective of the game was to create a fun environment for users to test and familiarize themselves with the topic of
aircraft system design and different architectures used, the game requirements can be defined.
\\
The game should introduce users to the concepts of redundancy and system failures, as well as different failure types such
as common-mode and common-cause failures.
The game has to have a good mix of fun and interactivity, while the sole purpose should not be entertainment, but rather a
mix of entertainment and education.
Education, in this context, is referred to as the part of awaking interest for a rather unknown topic.
Therefore, the game should be playable without any kind of knowledge regarding the topic of aircraft systems and should be easy
to get into.
Explanations and details should only be given as an addition, however should not be directly necessary to understand the basic concept
of gameplay.
It should be playable on open-door days, where it is not as pleasant to play the game only with mouse and keyboard, therefore a game pad
integration is necessary.

\section{Genre}\label{sec:genre}
The \textit{Puzzle} genre is chosen for the graphical user interface and interaction, while the major calculations for the
games' content may be categorized as \textit{Simulation}.

\section{Intended Gameplay}\label{sec:intended-gameplay}
The gameplay is described for a singular level, however the basic concept is the same for each level.
A level usually describes an aircraft system, the goal of the game is to finish or repair a given system.
In order to do that, the user needs to choose from a variety of given components to build the system in a way, that the
required safety level will be reached.
This can be done in different ways, however the efficiency (i.e.\ how many components were used in the building process) determine
the rating upon passing a level.
Upon starting a level, the user will face a grid-based puzzle with some set components such as sensors, computers, actuators
or cables.
The user may add new components by choosing them from a limited stack of given components.
Components cannot interfere with other components, however components may also be removed or replaced.
As soon as the user presses a button to simulate the system, a simulation process in the backend is triggered to calculate
the safety rating of the system built.
Based on the safety rating calculated, an animation is triggered that shows the performance of the user visually by starting, cruising
and landing a plane.
If the safety rating is too low, the level is not passed and can be replayed or modified, if the rating is above the given
threshold, the level is passed and another level can be chosen.
A score is then calculated, depending on the efficiency of the system (i.e.\ how close the user got to the given safety requirement) and
how many of the available components were used.
The score can be saved to a scoreboard.
Upon passing a level, further levels are unlocked, which provides a certain amount of progression through the game.

\\

It is also possible to create new levels in a sandbox style environment, where the user can choose different pre-defined components and
safety requirements to create a custom level.

\section{Game Mechanics}\label{sec:game-mechanics}
\todo{write}

\section{Graphic Design}\label{sec:graphic-design}
The goal of the graphic design process was to conceptualize the general layout of the game environment as well as the look and feel
of the major components used.
The graphics design process was iterative and most graphics have changed frequently throughout the game development process.
However, a list of elements that needed to be designed is given in section~\ref{subsec:list-of-components}.

\subsection{List of components}\label{subsec:list-of-components}
The following components need to be designed:
\begin{itemize}
    \item Screen backgrounds
    \item Background tiles
    \item Simulation components: actuator, sensor, computer, com-mon, cable, \ldots
    \item Build panel
    \item Requirement panel
\end{itemize}

\section{Sound Design}\label{sec:sound-design}
To provide atmosphere and create an 8 bit-styled experience, open source music will be used in the game.

\section{Language}\label{sec:language}
As the game is supposed to be used by a broad audience, especially in Germany and at the University Day of the University of Stuttgart, there should be an option
to change the language.
Since the audience is most likely to include young adults, teenagers and children, there are going to be multiple options even for a single language:
normal language and simplified language.
Furthermore, the game is designed to be understandable with a very low amount of reading text, however the text will always provide further information for interested people.
A language management system will be implemented which is based on using IDs (tags) instead of the actual text for any text string.
A processor is going to parse all available language files in XML format and a look-up table that maps each ID to the corresponding text string will be created.
Within the Rendering Engine, each text is going to be rendered in the language the game is set to.

\section{Game Engine Design}\label{sec:game-engine-design}
In this section, the framework and features the game engine should have are going to be detailed.

The next section, architecture~\ref{subsec:architecture}, gives an overview of the modular organization, layering and interconnectivity certain
components should provide.
In the features section~\ref{subsec:features}, the specific functionalities and capabilities will be explained.
\subsection{Architecture}\label{subsec:architecture}

\subsection{Features}\label{subsec:features}

\section{Game Environment Design}\label{sec:game-environment-design}
% describe the conception process of scenes, levels, ...

\section{Level Design}\label{sec:level-design}
The level design is a main part of this work, as the progression through the game and the process of explaining different concepts
within aircraft system design is heavily influenced by this.
Therefore, levels were conceptualized before the implementation, to have a guideline for the actual implementation.
Levels are categorized in difficulties, reaching from tutorial to hard.
When passing a level, the user unlocks new content (e.g. levels) to progress through the game.
Tutorials should guide the user through the features of this game and provide some insight on the basics of system design, so
it can be used at later stages of the game.
A visual representation of this is needed to provide enough input for younger age-groups to play and understand the game.
However, for other users, some more in-depth knowledge is also provided in order to better understand calculations, simulations and
game logic in the background.
Tutorial levels explain the basic usage, such as cable and component (re-)placement and the different safety requirement
categories.
The categories are described by colors, from red (catastrophic) to blue (no safety effect).
Each component that can be built in the level also has this information to it, so the user can visually see a representation
of the criticality and the effect of the objects to the system and its requirements.
Each level goal is defined by a safety requirement and a minimum count of correctly operating actuators (or other components, such
as flight control computers, sensors, \ldots).
As the user progresses through the levels, there will be harder goals in safety requirements that need to be solved by using
redundancy concepts or mechanisms such as voting.
As this work aims to explain most of the basic concepts, some levels should also take into consideration common-mode and common-cause
failures.
Here, the main goal is to provide insight into the differentiation of these, which can be done by using sensors of different types.

\\ \\

The following levels have been designed for this game by default:
\begin{enumerate}
    \item Tutorial 01: Connecting cables to components
    \item Tutorial 02: Rotating cables
    \item Tutorial 03: Using multiple cables on a grid tile
    \item Tutorial 04: Placing components
    \item Tutorial 05: Replacing components on the grid
    \item Enhancing a Simplex System
    \item Cross-connecting of Duplex System
    \item Multiple Actuators
    \item Actuator with 2 required correct signals
    \item Duplex Sensor
\end{enumerate}
\\
\\
Additionally, through a build mode the user is able to set up new levels including the requirements / level goal via the built-in
frontend, which then saves the level to a new xml file.
